%!TEX root = ../iotpaper.tex

\subsection{Gesture \& Motion Recognition on a Single Device}

Several efficient gesture-recognition algorithms already exist. Jiayang et al. \cite{Liu:2009, LiuuWave} presented an algorithm called uWave that is based on a single accelerometer. uWave quantizes the acceleration data to reduce computational load and uses dynamic time warping(DTW) to measure similarities between two time series of accelerometer data. Template adaptation deals with gesture variation over the time. Ahmad and Shahrokh \cite{Ahmad:2010} also proposes a gesture recognition system that uses only one 3-axis accelerometer. The system temporally compresses the acceleration time series to filter out variations not intrinsic to the gesture itself and reduces the size of the acceleration signals for next step of dynamic time warping. Then, the system uses affinity propagation to find a good set of exemplars from all data points. Finally, they implemented compressive sensing to recognize a repetition of a gesture. 

For the best user experience, gesture recognition should be in real-time and easy to use. Instead of using a button to indicate start time and end time of a gesture motion, Zoltan \cite{Zoltan} proposes an automatic segmentation method and uses two classification algorithms: Hidden Markov Models(HMM) and Support Vector Machine to to give high accuracy. This system has great performance and low response time, thus a good model for \gls{IoT} devices.

Considering the quadratic time and space complexity with DTW algorithm and the need of larger training sets with HMM, Zhe Ji et al. \cite{Ji:2015} proposed a new algorithm which uses FastDTW instead of DTW and HMM. Their algorithm is divided into two part: preprocess and classification. In the preprocessing step, the raw data is first filtered by a series of low-pass filters and its amplitude is normalized. Then, it is resampled to a fixed length. After preprocessing the raw data, FastDTW, which has linear time and space complexity, is used to calculated the alignment between two time series. Their work shows that the performance drop is not necessary and is avoidable while replacing lightweight FastDTW to DTW for reducing computational demand.