%!TEX root = ../iotpaper.tex

\section{Introduction}
\label{sec:Introduction}

In an \gls{IoT} environment, mobile devices may need to pair or authenticate themselves to other devices. However, unlike the traditional internet, an \gls{IoT} environment does not typically have a centralized certificate authority, making it difficult for one device to determine if another device is authentic. Furthermore, these \gls{IoT} devices are often resource-constrained, meaning traditional cryptographic defenses that support confidentiality, integrity, and authenticity difficult to implement \cite{cisco:iot-pf,authmodels}.

One potential solution to this problem is to use biometrics---particularly motion and gestures---in order to validate the identity of the device. Prior work has shown that impostors has a low probability of imitating a gesture calibrated to another person successfully \cite{Casanova}. Furthermore, motion recognition is suitable for \gls{IoT} systems which feature small sensors and low powered devices because motion recognition can achieve high accuracy with just an accelerometer \cite{RuizeXu}. 

Some prior work have looked at motion sensor data fusion across different devices to detect pairing, for example detecting device collision when tiling two tablets together \cite{SyncGes}. Existing work in gesture recognition and event detection focuses on gestures on the same device or similar devices (e.g. two tablets, gestures on a Wiimote \cite{LiuuWave}). However, pairing in an \gls{IoT} environment is usually needed for two asymmetric devices with different types of hardware sensors (e.g. a smartwatch with a smartphone).

In this project, we analyze the use of gestures as a biometric for peer-to-peer authentication in an \gls{IoT} scenario, where sensor devices are asymmetric. This asymmetry in device shape leads to different tendencies for holding the devices, and the difference in sensor accuracy and sampling rate also produces potential challenges for comparing gestures. Our key contributions are an experimental evaluation of gesture authentication on various devices including iPhones, Android devices, and a smartwatch.

The remainder of this paper is organized as follows. We start by defining our system defense and attack models in \autoref{sec:Attacks}. Next, we describe our experimental platform in \autoref{sec:Platform}. Our experiments are divided into two sections based on the defense models: Gesture Library (\autoref{sec:GestureLibrary}) and Simultaneous Gestures (\autoref{sec:Simultaneous}). In \autoref{sec:RelatedWork}, we described related work in biometrics for authentication and gesture recognition. Finally, we conclude the paper in \autoref{sec:Conclusion} and also describe future avenues of research for this method of authentication.