%!TEX root = ../iotpaper.tex

\subsection{Gesture \& Motion Recognition on a Single Device}

Several efficient gesture-recognition algorithms already exist. For accelerometer-based gesture recognition, Ali et al. \cite{Ali:2014} introduce and evaluate five cutting-edge algorithms, including \gls{DTW}, \gls{HMM}, \gls{SVM}, \gls{k-NN}, and \gls{ANN}. They evaluate these algorithms in both user-dependent and user-independent cases, and their result shows that \gls{DTW} and \gls{k-NN} achieve the best accuracy among other algorithms in both cases.

Jiayang et al. \cite{Liu:2009, LiuuWave} present an algorithm called uWave which is based on a single accelerometer. uWave quantizes the acceleration data to reduce computational load and uses \gls{DTW} to measure similarities between two time series of accelerometer data. Template adaptation deals with gesture variation over the time. To enhance the accuracy of user-independent recognition for some scenarios, Hussain and Rashid \cite{Hussain:2012} propose an enhancement based on modified uWave algorithm with hardware-accelerated DTW. Their implementation decouples the axes of gesture data while performing \gls{DTW} calculation to reduce the mismatch due to the variation of temporal speeds on different axes between two users. 

Aside from uWave, Ahmad and Shahrokh \cite{Ahmad:2010} also propose a gesture recognition system that uses only one 3-axis accelerometer. The system temporally compresses the acceleration time series to filter out variations not intrinsic to the gesture itself and reduces the size of the acceleration signals for next step of dynamic time warping. Then, the system uses affinity propagation to find a good set of exemplars from all data points. Finally, they implemented compressive sensing to recognize a repetition of a gesture. 

For the best user experience, gesture recognition should be in real-time and easy to use. Instead of using a button to indicate start time and end time of a gesture motion, Zoltan \cite{Zoltan} proposes an automatic segmentation method and uses two classification algorithms: \gls{HMM} and \gls{SVM} to to give high accuracy. This system has great performance and low response time.

Considering the quadratic time and space complexity with \gls{DTW} algorithm and the need of larger training sets with HMM, Zhe Ji et al. \cite{Ji:2015} propose a new algorithm which uses FastDTW instead of \gls{DTW} and \gls{HMM}. Their algorithm is divided into two parts: preprocess and classification. In the preprocessing step, the raw data is first filtered by a series of low-pass filters and its amplitude is normalized. Then, it is resampled to a fixed length. After preprocessing the raw data, FastDTW, which has linear time and space complexity, is used to calculated the alignment between two time series. Their work shows that the performance drop is not necessary and is avoidable while replacing lightweight FastDTW to \gls{DTW} for reducing computational demand.